An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
Spell check

---
title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
author:
  - name: Stephanie Kobakian
    affiliation: Queensland Univeristy of Technology
    email:  stephanie.kobakian@monash.edu
  - name: Dianne Cook
    affiliation: Monash University
    email:  dicook@monash.edu
abstract: >
  This algorithm creates a hexagon to represent each of the spatial polygons provided. It allocates these hexagon in a manner that preserves the spatial relationship of the areas. It showcases spatial distributions, by emphasising the small geograhical regions that are often diffcult to locate on large geographic maps.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

Spatial distrbutions have utilised alternative representations of geography for many years. In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.

@@

Spatial distributions of people and human related statistics can be misrepresented in geographic maps. Populations congregate around major cities and vertical living is increasingly common. Population statistics often requires dividing people into smaller, measureable areas. Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Comission hold the responsibility of the division. Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres. To divide the population equally, the square meterage of the geographic areas differ dramatically in size.

@@

Extremely small geographic areas are lost on large geographic maps, small inner areas of Sydney or Melbourne are not easily compared at a high level.
Cartograms place importance on the statistic of interest, allowing distorted map space on the display to represent differences in the statistic. These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geograhic area considered to be interesting. These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.

@@

The centre of the population hubs are used to distribute areas around the closest captial city.

@@

Begin with a set of polygons. The set should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object. We will use the Loca Goverment Areas of Tasmania, sourced from the Australian Bureau of Statistics.

@@

Each new hexagon will need to tesselate, a grid is created to ensure a close point is found, that will allow all areas to tesselate, this is inspired by tilegrams. The grid of possible hexagon centroids can be made using the `create_grid` function. The grid creation takes several steps. It requires the centroids, the hexagon size and the buffer distance.

@@

Allocation of all centroids can now take place using the set of polygon centroids and the hexagon map grid. 
For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
Allocate each centroid, beginning with the closest centroid to a focal point.
This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the captial, and the areas that are further will be accomodated after.

@@

Create a box of possible hexagon locations areoung the centroid. The bottom of the box will not be square as the buffer has already removed unnecessary points from over the ocean.

@@

The algorithm removes the outer corners of the square, creating a cricle of points, by only keeping points within a certain radius around the original centroid location.

@@

It is possible to use alternative maps to communicate spatial distributions.
Current methods do not always work for Australia due to the large gaps between denseley populated capital cities.

>>>>

---
title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
author:
  - name: Stephanie Kobakian
    affiliation: Queensland Univeristy of Technology
    email:  stephanie.kobakian@monash.edu
  - name: Dianne Cook
    affiliation: Monash University
    email:  dicook@monash.edu
abstract: >
  This algorithm creates a hexagon to represent each of the spatial polygons provided. It allocates these hexagon in a manner that preserves the spatial relationship of the areas. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on large geographic maps.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

Spatial distributions have utilised alternative representations of geography for many years. In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.

@@

Spatial distributions of people and human related statistics can be misrepresented in geographic maps. Populations congregate around major cities and vertical living is increasingly common. Population statistics often requires dividing people into smaller, measurable areas. Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Commission hold the responsibility of the division. Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres. To divide the population equally, the square meters of the geographic areas differ dramatically in size.

@@

Extremely small geographic areas are lost on large geographic maps, small inner areas of Sydney or Melbourne are not easily compared at a high level.
Cartograms place importance on the statistic of interest, allowing distorted map space on the display to represent differences in the statistic. These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geographic area considered to be interesting. These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.

@@

The centre of the population hubs are used to distribute areas around the closest capital city.

@@

Begin with a set of polygons. The set should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object. We will use the Local Government Areas of Tasmania, sourced from the Australian Bureau of Statistics.

@@

Each new hexagon will need to tessellate, a grid is created to ensure a close point is found, that will allow all areas to tessellate, this is inspired by tilegrams. The grid of possible hexagon centroids can be made using the `create_grid` function. The grid creation takes several steps. It requires the centroids, the hexagon size and the buffer distance.

@@

Allocation of all centroids can now take place using the set of polygon centroids and the hexagon map grid. 
For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
Allocate each centroid, beginning with the closest centroid to a focal point.
This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the capital, and the areas that are further will be accommodated after.

@@

Create a box of possible hexagon locations around the centroid. The bottom of the box will not be square as the buffer has already removed unnecessary points from over the ocean.

@@

The algorithm removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radius around the original centroid location.

@@

It is possible to use alternative maps to communicate spatial distributions.
Current methods do not always work for Australia due to the large gaps between densely populated capital cities.

### 2019-03-27 algorithmRjournal/algorithmRjournal.tex
Spell check

\abstract{%
This algorithm creates a hexagon to represent each of the spatial
polygons provided. It allocates these hexagon in a manner that preserves
the spatial relationship of the areas. It showcases spatial
distributions, by emphasising the small geograhical regions that are
often diffcult to locate on large geographic maps.
}

@@

Begin with a set of polygons. The set should be provided as an
\texttt{sf} object, this is a data frame containing a \texttt{geometry}
column. The \texttt{read\_shape} function can assist in creating this
object. We will use the Loca Goverment Areas of Tasmania, sourced from
the Australian Bureau of Statistics.

@@

Each new hexagon will need to tesselate, a grid is created to ensure a
close point is found, that will allow all areas to tesselate, this is
inspired by tilegrams. The grid of possible hexagon centroids can be
made using the \texttt{create\_grid} function. The grid creation takes
several steps. It requires the centroids, the hexagon size and the
buffer distance.

>>>>

\abstract{%
This algorithm creates a hexagon to represent each of the spatial
polygons provided. It allocates these hexagon in a manner that preserves
the spatial relationship of the areas. It showcases spatial
distributions, by emphasising the small geographical regions that are
often difficult to locate on large geographic maps.
}

@@

Begin with a set of polygons. The set should be provided as an
\texttt{sf} object, this is a data frame containing a \texttt{geometry}
column. The \texttt{read\_shape} function can assist in creating this
object. We will use the Local Government Areas of Tasmania, sourced from
the Australian Bureau of Statistics.

@@

Each new hexagon will need to tessellate, a grid is created to ensure a
close point is found, that will allow all areas to tessellate, this is
inspired by tilegrams. The grid of possible hexagon centroids can be
made using the \texttt{create\_grid} function. The grid creation takes
several steps. It requires the centroids, the hexagon size and the
buffer distance.
